\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-21 paper.tex
Updated the notations

\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n, p, k, m$ & number of observations, variables, embedding dimension, number of non-empty bins, respectively\\
$\mathbfit{X}, \mathbfit{x}$ & $p$-dimensional data (population, sample)\\
$\mathbfit{y}$ & $k$-dimensional layout\\
$P$ & orthonormal basis, generating a $d\text{-}dimensional$ linear projection of $p$-dimensional data\\
$T$ & true  model\\
\addlinespace
$g$ & functional mapping from \pD{} to \kD{}, especially as prescribed by NLDR\\
$\mathbfit{\theta}$ & (Hyper-) parameters for NLDR method\\
$r$ & ranges of the embedding components\\
$C^{(j)}$ & $j$-dimensional bin centers\\
$(b_1, b_2)$ & number of bins in each direction\\
\addlinespace
$(a_1, a_2)$ & binwidths, distance between centroids in each direction\\
$(s_1, \ s_2)$ & starting coordinates of the hexagonal grid\\
$q$ & buffer to ensure hexgrid covers data, proportion of data range, 0-1\\
$b$, $b'$ & total and non-empty hexagon bins in the grid\\
$n_k$ & number of observations within the $k^{th}$ hexagon\\
\bottomrule
\end{tabular}
\endgroup{}

>>>>

\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n, p, k, m$ & number of observations, variables, embedding dimension, number of non-empty bins, respectively\\
$\mathbfit{X}, \mathbfit{x}$ & $p$-dimensional data (population, sample)\\
$\mathbfit{y}$ & $k$-dimensional layout\\
$P$ & orthonormal basis, generating a $d\text{-}dimensional$ linear projection of $p$-dimensional data\\
$T$ & true  model\\
\addlinespace
$g$ & functional mapping from \pD{} to \kD{}, especially as prescribed by NLDR\\
$\mathbfit{\theta}$ & (Hyper-) parameters for NLDR method\\
$r$ & ranges of the embedding components\\
$C^{(j)}$ & $j$-dimensional bin centers\\
$(b_1, b_2)$ & number of bins in each direction\\
\addlinespace
$(a_1, a_2)$ & binwidths, distance between centroids in each direction\\
$(s_1, \ s_2)$ & starting coordinates of the hexagonal grid\\
$q$ & buffer to ensure hexgrid covers data, proportion of data range, 0-1\\
$b$, $b'$ & total and non-empty hexagon bins in the grid\\
$n_m$ & number of observations within the $m^{th}$ hexagon\\
\addlinespace
$h$ & hexagonal id\\
\bottomrule
\end{tabular}
\endgroup{}
